---
title: "Adding a New Hospital's Payer-Rate Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding a New Hospital's Payer-Rate Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

Like the other vignettes here, this file knits directly --
`rmarkdown::render("vignettes/adding-a-hospital-payer-rate.Rmd")` from the repository
root -- since this repository has no `DESCRIPTION` and is not built as an installed
package. The step-by-step *data-collection* process (finding a hospital's machine-readable
file, downloading it, flagging data-quality issues) is not itself R code and is covered
in full in `docs/vignettes/02_adding_a_new_hospital_payer_rate.md`; this vignette covers
the one part of that process that *is* real, executable R: loading the resulting table
with its enforced schema, and seeing exactly how a new row changes a real downstream
calculation.

```{r setup}
source("R/00_source_all.R")
model_parameters <- load_model_parameters("config/model_parameters.csv")
```

## The real 6-hospital table this model actually uses

`data/colonoscopy_multi_hospital_rates.csv` is the one hospital-rate table wired into an
R function -- `load_colonoscopy_hospital_rates_table()` reads it with an explicit
`col_types` spec, so a malformed or missing column fails loudly at load time rather than
silently producing `NA`s downstream.

```{r load-rates}
rates_table <- load_colonoscopy_hospital_rates_table()
rates_table
```

(The larger, 74-hospital `data/gyn_onc_hospital_payer_rates.csv` FREIDA-fellowship sample
is a standalone reference dataset with no R loader of its own -- it does not feed any
function in `R/`. See `docs/data_sources.md` and
`docs/vignettes/02_adding_a_new_hospital_payer_rate.md` for that dataset's own method.)

## What a new row actually feeds

```{r opportunity-cost}
opportunity_cost_bound <- compute_colonoscopy_opportunity_cost_bound(
  model_parameters, rates_table
)
opportunity_cost_bound
```

`opportunity_cost_ceiling` is the commercial-margin-based bound on what displacing a
colonoscopy-suite slot for a combined-EMB add-on could reasonably cost, at each real
hospital. This is the number a new hospital's row would actually change.

## Demonstration only: adding a hypothetical row

The row below is a made-up illustration, not real hospital data -- it exists only to show
the mechanics of adding a row and is never written to any file. A real addition must come
from an actual CMS price-transparency machine-readable file, with its own `source`
citation and confidence flags, exactly as every other row in this table does.

```{r demo-row}
demo_row <- tibble::tibble(
  state_abbr = "XX",
  hospital = "Example Hospital (demonstration only, not real data)",
  medicare_rate = rates_table$medicare_rate[1],
  commercial_mean_rate = rates_table$commercial_mean_rate[1] * 1.1,
  medicare_confidence = "not_applicable",
  commercial_confidence = "not_applicable",
  notes = "Synthetic row for vignette demonstration only -- never a real data point.",
  commercial_to_medicare_ratio = NA_real_,
  source = "vignette demonstration, not a real source"
)

rates_table_demo <- dplyr::bind_rows(rates_table, demo_row)

compute_colonoscopy_opportunity_cost_bound(model_parameters, rates_table_demo) %>%
  dplyr::filter(.data$hospital == demo_row$hospital)
```

That is the entire mechanism: a correctly-schemad row flows straight into
`compute_colonoscopy_opportunity_cost_bound()` with no code changes required. The real
work in adding a hospital is never the R code -- it is finding, downloading, and honestly
flagging the confidence of the underlying rate, which is why
`docs/vignettes/02_adding_a_new_hospital_payer_rate.md` spends almost all of its length on
that part instead of this one.

## Schema check worth running on any new row before committing it

```{r schema-check}
allowed_confidence <- c(
  "high", "medium_high", "medium", "low_medium", "low",
  "not_found", "inconclusive", "not_applicable"
)

rates_table %>%
  dplyr::filter(
    !.data$medicare_confidence %in% allowed_confidence |
      !.data$commercial_confidence %in% allowed_confidence
  )
```

An empty result (as above) means every row's confidence flags are in the allowed set --
run this same check against any new row before adding it, since a typo'd confidence
value (e.g. `"medim"` instead of `"medium"`) will not raise an error on its own, only
silently fail to mean anything downstream.
