---
title: "Evidence Tiers and Sensitivity Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Evidence Tiers and Sensitivity Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

As with the other vignettes in this directory, this repository is not an installed
package (no `DESCRIPTION`), so this file is knit directly --
`rmarkdown::render("vignettes/evidence-tiers-and-sensitivity.Rmd")` from the repository
root -- rather than built by `devtools::build_vignettes()`. The non-code narrative
covering the same ground is `docs/vignettes/03_interpreting_evidence_tiers_and_sensitivity.md`.

```{r setup}
source("R/00_source_all.R")
model_parameters <- load_model_parameters("config/model_parameters.csv")
price_index_table <- load_price_index_table("data/cpi_medical_care.csv")
```

## Evidence tiers: how sure is each input?

Every parameter carries an `evidence_tier`: `A` (Lynch-specific direct data), `B`
(contemporary U.S. public cost/reimbursement data), `C` (general/adjacent-population
literature), `D` (provisional placeholder), or `structural` (an analysis convention, not
an evidence claim).

```{r evidence-tiers}
summarize_evidence_tiers(model_parameters)
```

A tier is not a verdict on whether a number is usable -- it is a label on where the
number came from. Look at one tier-A parameter's full sourcing:

```{r one-parameter}
model_parameters %>%
  dplyr::filter(.data$parameter == "emb_failure_lynch") %>%
  dplyr::select(parameter, base_value, low_value, high_value, evidence_tier, source)
```

## Deterministic one-way sensitivity: which single parameter matters most?

Each of these parameters is varied alone, between its low and high bound, with every
other parameter held at its base value.

```{r one-way}
key_parameters <- c(
  "emb_office_professional_cost",
  "emb_failure_lynch",
  "combined_to_dnc_probability",
  "combined_emb_added_minutes",
  "direct_room_cost_per_minute",
  "anesthesia_cost_per_minute",
  "emb_pathology_cost",
  "dnc_facility_or_asc_fee",
  "coordination_cost",
  "emb_disposable_supply_cost"
)

sensitivity_estimates <- run_one_way_sensitivity(
  model_parameters,
  parameter_names = key_parameters,
  price_index_table = price_index_table
)

sensitivity_estimates %>%
  dplyr::arrange(dplyr::desc(.data$spread)) %>%
  dplyr::select(parameter, metric_at_low, metric_at_base, metric_at_high, spread)
```

The `spread` column is the tornado-bar length -- the widest row is the single parameter
this model's conclusion is most sensitive to. `figures/figure2_tornado.jpeg` is this
same table as a chart.

## Probabilistic sensitivity: how often does each strategy win when everything varies at once?

The committed `figures/figure4_psa_incremental_cost.jpeg` and
`tables/probabilistic_sensitivity_*.csv` files use 1,000 simulations; this vignette uses
200 so it knits quickly -- the mechanism is identical, just fewer draws.

```{r psa}
set.seed(1)
probabilistic_estimates <- run_probabilistic_sensitivity(
  model_parameters,
  price_index_table = price_index_table,
  n_simulations = 200
)

probability_cheapest <- summarize_probability_cheapest(probabilistic_estimates)
probability_cheapest
```

## Reading the two together

A parameter can be well-sourced (tier A) and still have a wide low/high range, if the
underlying studies disagreed with each other -- that is honest uncertainty, not a
documentation gap. A parameter can be a tier-D placeholder and still barely move the
tornado plot, in which case its missing source is a lower priority to fix than a tier-C
parameter that *does* produce a wide bar. Cross-reference the tier table above against
the `spread` column above to find out, right now, which of this model's least-sourced
parameters would most reward a better source:

```{r cross-reference}
model_parameters %>%
  dplyr::filter(.data$parameter %in% key_parameters) %>%
  dplyr::select(parameter, evidence_tier) %>%
  dplyr::left_join(
    sensitivity_estimates %>% dplyr::select(parameter, spread),
    by = "parameter"
  ) %>%
  dplyr::arrange(dplyr::desc(.data$spread))
```
