---
title: "Mapping the Hospital MRF Sample"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mapping the Hospital MRF Sample}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

As with the other vignettes in this directory, this repository is not an installed
package (no `DESCRIPTION`), so this file knits directly --
`rmarkdown::render("vignettes/mapping-hospital-mrf-sample.Rmd")` from the repository
root -- rather than through `devtools::build_vignettes()`. The hospital-level list this
map summarizes is documented in full, with every hospital's name and outcome, in
`docs/mrf_hospital_data_overview.md`; this vignette covers the map itself.

```{r setup}
source("R/00_source_all.R")
```

## Load both real-hospital MRF samples

```{r load-data}
hospital_payer_rates <- readr::read_csv(
  "data/gyn_onc_hospital_payer_rates.csv", show_col_types = FALSE
)
colonoscopy_hospital_rates <- load_colonoscopy_hospital_rates_table()

nrow(hospital_payer_rates)
nrow(colonoscopy_hospital_rates)
```

## Classify each FREIDA-sample hospital's data as usable or not

A hospital-code row counts as usable if either confidence column is anything other than
`not_found`/`inconclusive`/`not_applicable` -- the same rule documented in
`docs/mrf_hospital_data_overview.md`.

```{r classify}
freida_classified <- classify_freida_hospitals(hospital_payer_rates)
freida_classified

table(freida_classified$has_usable_data)
```

## Build one row per hospital, with approximate coordinates

Unions the FREIDA-sample hospitals with any usable data with the original 6-hospital
sample, de-duplicating hospitals that appear in both (UCHealth University of Colorado
Hospital, Emory University Hospital, and NYU Langone Hospitals (Tisch)), then joins each
hospital to its home city's approximate coordinates from
`data/gyn_onc_hospital_cities.csv`. Those coordinates come from the U.S. Census Bureau's
2024 Gazetteer Files -- the real internal-point coordinate of each hospital's home city,
not a geocoded street address (see that CSV's own `coordinate_source` column for which of
three methods applies to each row: an exact Census place match, a county centroid for the
two NYC-borough hospitals that aren't their own Census place, or the nearest incorporated
city for La Jolla, CA, which is an unincorporated San Diego neighborhood).

```{r build-points}
hospital_points <- build_hospital_mrf_points(
  hospital_payer_rates, colonoscopy_hospital_rates
)
hospital_points %>% dplyr::arrange(.data$state)

nrow(hospital_points)
dplyr::n_distinct(hospital_points$state)
table(hospital_points$coverage)
```

## The map

Hospitals that share a city (e.g. four in New York City) plot at the same underlying
coordinate; `plot_hospital_mrf_map()` jitters them with a fixed seed so every hospital is
visible as its own point, and says so in the plot's own subtitle.

```{r plot, fig.width = 9, fig.height = 6}
plot_hospital_mrf_map(hospital_points)
```

This is exactly what `analysis/19_hospital_mrf_map.R` saves to
`figures/figure8_hospital_mrf_map.jpeg` and what `README.md`'s "Hospital
price-transparency (MRF) sample" section embeds as Figure 5.

## Where to go next

- `docs/mrf_hospital_data_overview.md` -- the full hospital-by-hospital list (including
  the 7 hospitals attempted but excluded here for lacking usable data, and why)
- `vignettes/adding-a-hospital-payer-rate.Rmd` -- extending either sample with a new
  hospital
