---
title: "Running the Base-Case Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running the Base-Case Model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

This repository is a collection of sourced `R/` files rather than an installed package
(see `R/00_source_all.R`'s own docblock) -- there is no `DESCRIPTION`, so this vignette
cannot be built with `devtools::build_vignettes()` the way a real package's vignettes
would be. It is written in the standard R-package vignette format anyway (YAML
`vignette:` block, knittable code chunks) so it reads the same way, and it knits
directly with `rmarkdown::render("vignettes/running-the-base-case.Rmd")` from the
repository root. The narrative, non-code walkthrough of the same material lives in
`docs/vignettes/01_running_the_base_case.md`, if you'd rather read it without running R.

## Load every model function

```{r setup}
source("R/00_source_all.R")
```

## Load the parameter table and the price index

Every dollar figure and every probability this model uses comes from one CSV --
`config/model_parameters.csv` -- not from anything hardcoded in `R/`.

```{r load-parameters}
model_parameters <- load_model_parameters("config/model_parameters.csv")
price_index_table <- load_price_index_table("data/cpi_medical_care.csv")

nrow(model_parameters)
table(model_parameters$evidence_tier)
```

## Compute the three strategies' costs

```{r compute-strategies}
strategy_result <- compute_strategy_costs(model_parameters, price_index_table)
strategy_result$strategy_costs
```

`strategy_result$cost_components` has the same result broken into line items
(professional fee, pathology, anesthesia, facility fee) instead of one total per
strategy:

```{r cost-components}
strategy_result$cost_components
```

## Compare the strategies

```{r compare}
strategy_comparison <- compare_strategies_to_cheapest(strategy_result$strategy_costs)
strategy_comparison

combined_vs_office <- compare_combined_vs_office(strategy_result$strategy_costs)
combined_vs_office
```

## The threshold question and the auto-generated summary sentence

```{r threshold-and-sentence}
threshold_estimates <- run_threshold_analyses(model_parameters, price_index_table)

summary_sentence <- build_summary_sentence(
  strategy_comparison, combined_vs_office, threshold_estimates
)
cat(summary_sentence)
```

This is the exact sentence `analysis/01_base_case.R` writes to
`tables/summary_sentence.txt` and that `README.md`'s "What the base case currently
shows" section quotes -- generated from live model output here, not copied. If you
change a parameter in `config/model_parameters.csv` and re-knit this vignette, this
sentence changes with it.

## Where to go next

- `vignettes/evidence-tiers-and-sensitivity.Rmd` -- how sure is each input, and how much
  does the result move when you vary it
- `docs/clinical_coding_reference.md` -- which CPT/HCPCS code backs each cost parameter
  used above
- `docs/resident_onboarding.md` -- a plain-language start-here guide if this is your
  first time in this repository
